### 2017-06-07 Doc/classicthesis/Chapters/Conclusions.tex
Analysis
state of the art: recopilation
design init
design arch
impl avance
finishing touches
First draft

To finish this document, we sum up some conclusions from the work done, and results 
obtained. We will also enumerate some future lines of research that could start from
the work done in this project.

@@

The designed solution for the integration of Idemix and the Internet of Things provides new possibilities for the IoT security field, mainly in those scenarios where people's data is more vulnerable. However, there is a long path of research before we can see this in production. Many decisions depend on the specific deployment in course, and our solution tries to ease the best it all that future process.

With regards to the designed architecture, the flexibility of the Computation Offloading technique, identifying the key operations that can't be delegated, and those ones that can, allows us to define a general solution for the vast world of the Internet of Things. The IoT devices can operate as individual actors in the Idemix ecosystem. When in need of performing offloading, the delegation server also falls into the IoT class of devices, a great benefit for any real project, having as many options as possible, the solution delivered can be adapted to most of requirements. Nevertheless, being so open to any solution leaves us with a lot of work to do, researching what are the best options, comparing benefits and drawbacks.

Our PoC implementation demonstrates that this project is actually feasible, not by performing a simulation of an IoT device, like in \citep{vanet}. During its development, we had to investigate a lot of concepts related to IoT, smart cards, and even the insides of P2ABCE's code, to fix many existing bugs in the original project and minimize the amount of changes it had to undergo, in order to work with the IoT devices.

@@

% Mejoras PoC
% Mejoras arquitectura: estudiar entornos típicos IoT y definir un despliegue realista usando esta cryptografía

>>>>

To finish this document, we sum up some conclusions from the work done, and results 
obtained. We will also enumerate some future lines of research.

@@

In the memory of this project we try to show the work done from the beginning, but we only showed our right decisions, and the information that is significant for the final result. The truth is that, aside from the information included in this paper, we have worked with other systems that ended up discarded. This isn't a negative aspect, because if we didn't, for example, study the Contiki OS, Cooja simulator and the hardware used, we could not be sure the development of the first PoC for that system would be impossible in the time given.

With regard to the work presented, the flexibility of the computation offloading technique, identifying the key operations that can be delegated, and those ones that can't, has allowed us to define a general solution for the vast world of the Internet of Things. The IoT devices can operate as individual actors in the P2ABCE ecosystem, and when in need of performing computation offloading, the delegation server can also be a device considered into the IoT class.

% Resultados son válidos: feseability, problema de tiempo en sistemas de tiempo real
% Se han conseguido objetivos planteados
% Experiencia: qué era más tedioso, dificultades durante diseño y desarrollo
% Primera aproximación de este tipo ~~: más bien somos el future work de...
% Aplicación de procedimientos aprendidos/aplicados durante el TFG/carrera
% ^ Novelty

During the development, we had to investigate a lot of concepts related to IoT, smart cards, and even the insides of P2ABCE's code, to fix many existing bugs in the original project and minimize the amount of changes it had to undergo, in order to work with the IoT devices. In the implementation chapter we give guidelines to port MULTOS applications, considering the particularities we encountered, that's why we can't consider it an \textit{instruction manual to port MULTOS apps}, but an interesting reading on how to confront a similar project. For example, if we wanted the Idemix implementation from \citep{vullers2013efficient}, previous to P2ABCE, in a IoT device, we could apply almost the same steps, obtaining a core functionality of Idemix for constrained devices in C.

Our PoC implementation demonstrates that this project is actually feasible, not by performing a simulation of an IoT device, like in \citep{vanet}. However, the use of third party libraries and no hardware acceleration support, makes the PoC too slow for certain cases, e.g., a Real-Time system requires almost immediate operations, like a car warning that another one is approaching too fast.
There is a long path of research before we can see this design in production, as many decisions depend on the specific deployment in consideration.

Recalling the objectives listed in \autoref{objectives:section}, we think we accomplish them, except the implementation of a PoC in the most constrained device possible, where we used LEDE to ease our development, and the last objective, where we could have given a use to the PoC, and we leave as part of the future work.

@@

Due to the nature of the project, there exist many options to continue researching in this area. We list below a collection of the tasks we couldn't accomplish but would have been our next steps:

\begin{itemize}
	\item Second PoC for Arduino systems

	We have already developed a working PoC for Linux based systems, and from our objective of using the most constrained devices available, we can follow an iterative process, building for devices a little more constrained than the last one. The next natural step, after building with LEDE/OpenWrt, is to aim for Arduino.

	The critical changes to the actual PoC are: 
	\subitem The transmission channel, if the device has no TCP/IP stack, it could use a Serial connection to transmit BIOSC and delegation messages.
	\subitem The use of a Json file to store the smart card status depends on whether the device has enough space or a file system. The current Json parser also uses too much dynamic memory. At this stage the serialization should be performed in a binary format, in a file or writing variables directly to the EEPROM memory.
	\subitem GMPLib and OpenSSL libraries must be replaced by others with similar capabilities, or special implementations for the particular device in use.

	All these changes affect only the \textit{external utilities} and \textit{interfaces} sections of the code, leaving the \textit{core} untouched, because the smart card logic doesn't change.

	\item Implement more P2ABCE functionality in the device

	If instead of aiming for more constrained devices, we work with similar devices to the Omega2, the computational power of the device could assume all the functionality of P2ABCE, at least for some roles. In a M2M (machine to machine) environment, the devices could act as Provers and Verifiers in the same interaction, and the verifying logic could be implemented entirely in the device (generate a Presentation Policy and checking a prove in a Presentation Token is valid), reducing the need of a delegation server.

	\item Improve the \textit{core smart card} code

	From the simple refactoring of removing the MULTOS reimplemented API for direct calls to the \textit{interfaces}, to identify all the \texttt{memcpy} copies of multiple variables with one call, removing the compiler directive for not using memory padding in the defined structures, letting the compiler manage the memory automatically.

	\item Support Extended APDUs

	Currently, the APDU instruction handlers use the GET RESPONSE command to send large APDU Response Payloads, but we can reduce the number of APDUs exchanged supporting the Extended APDU format. Because the P2ABCE already sent some Extended APDUs, the APDU I/O interface in the PoC has support for Extended APDU Commands, but not for Extended Responses.

	\item Integrate the IoT+Idemix solution in other system

	Our seventh objective, that we couldn't get to design in depth. The original idea was to integrate in a FIWARE\footnote{FIWARE \url{https://www.fiware.org/}} environment the Fiware Keyrock and Idemix Issuer, so both, users and IoT devices' identities are managed in the IdM\footnote{Identity Management - KeyRock \url{https://catalogue.fiware.org/enablers/identity-management-keyrock}} system. The Issuer generates credentials based on the user’s attributes held in the Keyrock, and IoT devices can authenticate against Fi-ware services (using Idemix), or authenticate against other IoT devices (M2M).

	\begin{figure}[bth]
		\begin{center}
			\includegraphics[width=0.8\linewidth]{gfx/fiware}
		\end{center}
		\caption{IoT+Idemix Fi-Ware integration.}
		\label{fig:fiware}
	\end{figure}

\end{itemize}

% Último objetivo: FIWARE

### 2017-06-07 Doc/classicthesis/Chapters/Introduction.tex
First draft

Many of this objectives require the use of a great amount of data, and thanks to organizations like \href{https://wikileaks.org/}{WikiLeaks}, people are aware of the implications of their data on the Internet, demanding more security and privacy for it. This includes not only the data shared with others, where one must trust they will keep it safe, but it's also the data collected about us and that we don't have direct control over it. The attack Sony suffered in 2011 to PSN \citep{PSN2011} is an example of the trust people had in Sony to store their billing information, and because the security of that information depended on both them and Sony, people found themselves compromised unable to do anything about it.

@@

The goal of this project is to integrate Idemix with the IoT. It will be done using the ABC4Trust's \ac{P2ABCE}, a framework that defines a common architecture, policy language and data artifacts for an attribute based ecosystem, cryptographically based on either IBM's Idemix or Microsoft's U-Prove \citep{p2abcurl}. This gives us a standardized language to exchange Idemix's messages between IoT devices and any other P2ABCE actor.

>>>>

Many of this objectives require the use of a great amount of data, and thanks to organizations like \href{https://wikileaks.org/}{WikiLeaks}, people are aware of the implications of their data on the Internet, demanding more security and privacy for it. This includes not only the data shared with others, where one must trust they will keep it safe, but it's also the data collected about us and that we don't have direct control over it. The attack Sony suffered in 2011 to PSN\footnote{2011 PlayStation Network outage - 
\url{https://en.wikipedia.org/wiki/2011_PlayStation_Network_outage}} is an example of the trust people had in Sony to store their billing information, and because the security of that information depended on both them and Sony, people found themselves compromised unable to do anything about it.

@@

The goal of this project is to integrate Idemix with the IoT. It will be done using the ABC4Trust's \ac{P2ABCE}, a framework that defines a common architecture, policy language and data artifacts for an attribute based ecosystem, cryptographically based on either IBM's Idemix or Microsoft's U-Prove \footnote{P2ABCEngine \url{https://github.com/p2abcengine/p2abcengine}}. This gives us a standardized language to exchange Idemix's messages between IoT devices and any other P2ABCE actor.

### 2017-06-07 Doc/classicthesis/Chapters/Objectives.tex
First draft

\section{Project description}

@@

In the P2ABCE repository \citep{p2abcurl} there is available the project's code, divided in two solutions: a complete P2ABCE implementation in Java and a MULTOS smart card implementation as PoC for the project.

@@

MULTOS is a multi-application smart card operative system, which provides a custom developing environment, with rich documentation \citep{MultosTechLib}. MULTOS smart cards communicate like any other smart card following the standard, but internally offers a very specific architecture, affecting the way one must code applications for it.

@@

With regards to primitive types, to avoid confusion with their sizes, MULTOS defines and uses the following data types specified in \autoref{fig:multosDataTypes}. It's important to notice that MULTOS is Big Endian
\marginpar{\includegraphics[width=\linewidth]{gfx/Big-Endian}\\Big-Endian, Wikipedia}
and when storing structures there is no padding between defined variables, unlike modern compilers that perform data structure alignment \citep{dataStructAlign} for performance.

@@

Nevertheless, the C-API documentation \citep{MultosTechLib} provides rich description for each function.

@@

For this reason, the current \ac{PoC} is developed on LEDE, Linux Embedded Development Environment \citep{ledeproject}, using the Onion Omega2 development board. Although the Omega2 uses LEDE, its microcontroller is also listed as compatible with ThreadX OS \citep{THREADX}, a Real-Time Operative System for embedded devices, therefore, the performance measured in our PoC can be relevant to real scenarios with similar hardware.

>>>>

\section{Project description}\label{objectives:section}

@@

In the P2ABCE repository\footnote{\url{https://github.com/p2abcengine/p2abcengine}} there is available the project's code, divided in two solutions: a complete P2ABCE implementation in Java and a MULTOS smart card implementation as PoC for the project.

@@

MULTOS is a multi-application smart card operative system, which provides a custom developing environment, with rich documentation\footnote{MULTOS technical library - \url{http://www.multos.com/developer_centre/technical_library/}}. MULTOS smart cards communicate like any other smart card following the standard, but internally offers a very specific architecture, affecting the way one must code applications for it.

@@

With regards to primitive types, to avoid confusion with their sizes, MULTOS defines and uses the following data types specified in \autoref{fig:multosDataTypes}. It's important to notice that MULTOS is Big Endian
\marginpar{\includegraphics[width=\linewidth]{gfx/Big-Endian}\\Big-Endian, Wikipedia}
and when storing structures there is no padding between defined variables, unlike modern compilers that perform data structure alignment \footnote{\url{https://en.wikipedia.org/wiki/Data_structure_alignment}} for performance.

@@

Nevertheless, the C-API documentation\footnote{\url{http://www.multos.com/developer_centre/technical_library/}} provides rich description for each function.

@@

For this reason, the current \ac{PoC} is developed on LEDE\footnote{Linux Embedded Development Environment - \url{https://lede-project.org/}} using the Onion Omega2 development board. Although the Omega2 uses LEDE, its microcontroller is also listed as compatible with ThreadX\footnote{THREADX Real-Time Operative System for embedded devices - \url{http://rtos.com/products/threadx/}}, therefore, the performance measured in our PoC can be relevant to real scenarios with similar hardware.

### 2017-06-07 Doc/classicthesis/Chapters/Validation.tex
First draft

\begin{table}[h]
	\myfloatalign
	\begin{tabularx}{0.75\textwidth}{ll} \toprule
		MCU & Mediatek MT688 \citep{MT7688} \\
		CPU & MIPS32 24KEc 580MHz \\
		RAM & 64MB \\
		Storage & 16MB \\
		Firmware & LEDE (OpenWRT fork distro) \\
		Connectivity & Wifi b/g/n \\
		Power & 3.3V 300mA \\
		\bottomrule
	\end{tabularx}
	\caption[Onion Omega 2 Specifications]{Onion Omega2 Specifications.}
	\label{tab:Omega2Specs}
\end{table}

>>>>

\begin{table}[h]
	\myfloatalign
	\begin{tabularx}{0.75\textwidth}{ll} \toprule
		MCU & Mediatek MT688\footnote{MediaTek MT7688 Datasheet - \url{https://goo.gl/kqD2gF}} \\
		CPU & MIPS32 24KEc 580MHz \\
		RAM & 64MB \\
		Storage & 16MB \\
		Firmware & LEDE (OpenWRT fork distro) \\
		Connectivity & Wifi b/g/n \\
		Power & 3.3V 300mA \\
		\bottomrule
	\end{tabularx}
	\caption[Onion Omega 2 Specifications]{Onion Omega2 Specifications.}
	\label{tab:Omega2Specs}
\end{table}
